---
title: "CodeBook"
output: html_document
date: "2023-03-28"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Column Transformations

Columns in the original data were removed to only include means and standard deviations. Variables were made more readable in English and given descriptive names. Finally, both a column for the subjects of the experiments and the specific activity were added to the data. The activities were given a readable name. The variables after the transformation are:

```{r run_analysis}
colnames(fullx)
```

## Combining Train and Test Data

After this process was performed on the training data, it was performed on the test data. Finally, the data was merged into a single dataframe including all observations

## Creating Tidy Means by Subject and Activity

Finally, using apply() and some fore loops I created a dataframe that had a summary of the means for every variable for a single subject and a summary of every variable for a single activity. These were given unique identifiers of the subject or the activity for the observations. Finally it was exported as a .txt file named "tidy.txt"

The variable names are:

```{r run_analysis}
colnames(temp)
```